Supplemental Appendix for ``An asymptotically normal out-of-sample test of equal predictive accuracy for nested models''

### 2014-11-04 appendix.tex
Revise theoretical component of paper

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.}\\%
  Iowa State University}

@@

\newcommand{\WesA}[1][]{\ocltb{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1}(F_t^{#1}) \osumb{t} (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\ocltb{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}

@@

\noindent%
This appendix contains mathematical proofs and some supporting Lemmas
for the paper, ``An asymptotically normal out-of-sample test of equal
predictive accuracy for nested models.''
Define the additional notation 
$f_t = f_t(\btrue)$,
$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
$F_t = F_t(\btrue)$,
$h_t = h_t(\btrue)$,
and
\begin{equation*}
  H_{t} = \tfrac1t \sum_{s=1}^t h_{s}.
\end{equation*}
All of the proofs in this section will be presented for the case where
there is a single alternative model. The Cram\'er-Wold device ensures
that the corresponding multivariate results follow trivially.

\begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
\begin{proof}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation*}
    \sqrt{P} (\fb - \E \fb(\btrue))
    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
  \end{equation*}
  Lemma~\ref{res:a1} ensures that the second term is $o_p(1)$, and
  we can rewrite this summation as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb(\btrue))
    &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.

  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. Finally,
  \begin{equation*}
    \oclt{t} (f_t - \E f_t,\ H_t)' \to^d N(0, S)
  \end{equation*}
  using the same argument as \citet{Wes:96}.
\end{proof}

\begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
\begin{proof}
  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
  \citet{RoW:05} complete the proof.
\end{proof}

@@

\begin{proof}
  We can rewrite this summation as
  \begin{multline*}
    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
    \ocltc{t} 2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue)
    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
  \end{multline*}
  Each of these individual summations can be shown to converge to
  zero in probability. First,
  \begin{equation*}
    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
    = O(R'/\sqrt{P}).
  \end{equation*}
  Also,
  \begin{align*}
    \Big\lvert \ocltc{t} &2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
    &\leq \ocltc{t} 2 \big\lvert (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t' \big\rvert
    \max_{t=R+1,\dots,R'} \lvert  \bh_t - \btrue \rvert \\
    & = O_p(R'/\sqrt{P})
  \end{align*}
  and
  \begin{equation*}
    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
    \leq \ocltc{t} \lvert x_t'x_t \rvert \max_{t=R+1,\dots,R'} (\bh_t - \btrue)'(\bh_t - \btrue)
    = O_p(R'/\sqrt{P}).
  \end{equation*}
  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
  construction, this completes the proof.
\end{proof}

\begin{alem}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and Assumptions~\ref{a1} -- \ref{a4}
  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
  \infty$ and $R' = o(\sqrt{P})$. Then
  \begin{enumerate}
  \item $\sup_{t=R'+1,\dots,T} | t^a H_t | \to^p 0$.
  \item $\sup_{t=R+1,\dots,R'} | t^a H_t | = O_p(1)$.
  \item $\sup_{t = R'+1,\dots,T} | t^a(\bh_t - \btrue) | \to^{p} 0$.
  \item $\sup_{t = R+1,\dots,R'} | t^a(\bh_t - \btrue) | = O_p(1)$.
  \end{enumerate}
\end{alem}

\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
    the same mixing process as the original variables) by
    Assumption~\ref{a3}, and the moment and size conditions in that
    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
    \begin{equation}\label{eq:2}
      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
    \end{equation}
    where $W(\cdot)$ is a multivariate Gaussian process.

    If $t/T \to \gamma$ then $T^{1/2} / t^{1-a} \to 0$ and the limit
    in~\eqref{eq:2} is almost surely 0. If $t/T \to 0$, then
    \begin{equation*}
      \E\Big( t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big)^2 = t^{2a - 1}\, O(1)
    \end{equation*}
    and the limit in~\eqref{eq:2} is again almost surely 0. The
    Continuous Mapping Theorem then implies that
    \begin{equation*}
      \sup_{t=R'+1,\dots,T} \Big| t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big| \to^p 0.
    \end{equation*}
  \item Again, $x_{t-1} \ep_t$ is an $L_2$-mixingale of size
    $-1/2$. As a result, we can use a maximal inequality of
    \cite{Mcl:75} (also available as Corollary 16.10 in
    \citealp{Dav:94}), giving
    \begin{align*}
      \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s\Big)^2 \Big\rvert
      &\leq \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(\sum_{s=2}^t s^{a-1} x_{s-1} \ep_s\Big)^2 \Big\rvert \\
      &= O(1) \sum_{s=2}^{R'} s^{2a - 2}
    \end{align*}
    which converges to a finite limit.
  \item We have
    \begin{multline*}
      \sup_{t=R'+1,\dots,T} | t^a (\hat{\beta}_t - \btrue) | \leq \\
      \sup_{t,u =R'+1,\dots,T} \Big| [ \hat{B}_u - B]
      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R'+1,\dots,T} \Big|
      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|
    \end{multline*}
    and both terms converge to zero in probability by Part 1 and by
    assumption.
  \item Similar to the previous argument, we have
    \begin{multline*}
      \sup_{t=R+1,\dots,R'} | t^a (\hat{\beta}_t - \btrue) | \leq \\
      \sup_{t,u =R+1,\dots,R'} \Big| [ \hat{B}_u - B]
      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R+1,\dots,R'} \Big|
      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|.
    \end{multline*}
    Both terms are $O_p(1)$ by Part 2 and by assumption. \qedhere
  \end{enumerate}
\end{proof}

@@

\begin{proof}
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lvert \ocltb{t} (F_t - \E F_t) B \Big\rvert
  \sup_{t = R'+1,\dots,T} | H_t |.
\end{equation*}
From Lemma~\ref{res:a2}, $\sup_{t = R'+1,\dots,T} | H_t | \to^p 0$. The \clt\ implies
that $\ocltb{t} (F_t - \E F_t) = O_p(1)$,
establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
and~\eqref{eq:13} are similar.
\end{proof}

\bibliography{texextra/AllRefs}
\end{document}

>>>>

\author{Gray Calhoun\thanks{Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.}\\%
  Iowa State University}

@@

\newcommand{\WesA}[1][]{\ocltb{t}
  (F_t^{#1} - F) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\ocltb{t}
  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}

@@

\noindent%
This appendix contains mathematical proofs and some supporting Lemmas
for the paper, ``An asymptotically normal out-of-sample test of equal
predictive accuracy for nested models.''  Define the following
additional terms:
\begin{equation*}
  F_t(\beta) = (4 x_t'\beta - 2 y_{t+1} - 2 \yh_{t+1}) x_t',
\end{equation*}
$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
$H_t = \sum_{s=1}^{t-1} x_t \ep_{t+1} / (t-1)$.
And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.

\begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
\begin{proof}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation}\label{eq:6}
    \sqrt{P} (\fb - \E \fb^*)
    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
  \end{equation}
  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
  we can use a Taylor expansion to rewrite~\eqref{eq:6} as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb^*)
    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. The proof that
  \begin{equation*}
    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
  \end{equation*}
  follows the same argument as in \citet{Wes:96}.
\end{proof}

\begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
We will only prove $\sigmah_2 \to^p \sigma$. The result for
$\sigmah_1$ is essentially the same, but uses \citepos{JoD:00} Theorem
2.1 instead of an application of the \lln.
\begin{proof}
  First, we can rewrite the components of the variance estimator as
  \begin{align*}
    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
    \intertext{and}
    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
  \end{align*}
  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
  $\fb - \E \fb^* \to^p 0$,
  $\gb - \E \gb^* \to^p 0$,
  \begin{gather}
    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
    \intertext{and}
    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
  \end{gather}
  The first two results are implied by the proof of Theorem~\ref{res:1}
  and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7} follow from the \lln, so it
  suffices to prove~\eqref{eq:4} and~\eqref{eq:5}.

  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
  that~\eqref{eq:4} holds if
  \begin{gather}
    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
    \intertext{and}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
  \end{gather}
  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
  \begin{align*}
    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  by Lemma~\ref{res:a2} and the \lln.
  A similar argument holds for the second term:
  \begin{align*}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big) (2 x_t'\btrue - y_{t+1} - \yh_{t+1}) \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
\end{proof}

@@

\begin{proof}
  We can rewrite this summation as
  \begin{multline*}
    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
  \end{multline*}
  Each of these individual summations can be shown to converge to
  zero in probability. First,
  \begin{equation*}
    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
    = O(R'/\sqrt{P}).
  \end{equation*}
  Also,
  \begin{align*}
    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t' \big\rVert
    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
    & = O_p(R'/\sqrt{P})
  \end{align*}
  and
  \begin{equation*}
    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
    = O_p(R'/\sqrt{P}).
  \end{equation*}
  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
  construction, this completes the proof.
\end{proof}

\begin{alem}\label{res:a2}
  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
  \infty$ and $R' = o(\sqrt{P})$. Then
  \begin{enumerate}
  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
  \item $\omaxb{t} | B_t - B | \to^p 0$,
  \item $\omaxc{t} | B_t - B | = O_p(1)$,
  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
  \end{enumerate}
  where the absolute value is taken as the largest of the
  element-by-element absolute values.
\end{alem}

This Lemma establishes that \citepos{Wes:96} basic results hold under
our weaker moment and dependence conditions and provides several
extensions. To streamline the presentation, we'll assume in these
proofs that $x_t$ is a scalar.
\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
    of size $-1/2$; let $c_t$ and $\zeta_k$ denote its mixingale
    constants and coefficients. Note that $t^{a-1} x_t \ep_{t+1}$ is
    also an $L_2$-mixingale array with constants $t^{a-1} c_s$ and
    coefficients $\zeta_k$, since
    \begin{align*}
      \| \E_{t-k} x_t \ep_{t+1} t^{a-1} \| &= t^{a-1} \| \E_{t-k} x_t \ep_{t+1} \| \\
      &\leq (t^{a-1} c_t) \zeta_k
    \end{align*}
    and
    \begin{align*}
      \| x_t \ep_{t+1} t^{a-1} - \E_{t+k} x_t \ep_{t+1} t^{a-1} \| &= t^{a-1} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
      &\leq (t^{a-1} c_t) \zeta_{k+1}.
    \end{align*}

    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
    \begin{align*}
      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta/2} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2a - 2 + \delta}
    \end{align*}
    where the second inequality follows from \citepos{Mcl:75} maximal
    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
    Corollary 16.10). The summation converges to a constant as $T \to
    \infty$ and $(R'-1)^{-\delta} \to 0$, completing the proof.

  \item As in Part 1, $x_t \ep_{t+1} t^{a-1}$ is an $L_2$-mixingale of size
    $-1/2$ and we can use \citepos{Mcl:75} maximal inequality to get
    \begin{align*}
      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
    \end{align*}
    which again converges to a finite limit.
  \item The same argument used in Part 1 implies that $\omaxb{t} |
    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
    the result follows.
  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
  \item We have
    \begin{align*}
      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
      &\leq \omaxb{t} |\hat{B}_t - B|
      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
    \end{align*}
    and both terms converge to zero in probability by Parts 1 and 3.
  \item Similar to the previous argument, we have
    \begin{align*}
      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
    \end{align*}
    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
  \end{enumerate}
\end{proof}

@@

\begin{proof}
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lVert \ocltb{t} (F_t - F) B \Big\rVert \;
  \omaxb{t} \lVert H_t \rVert.
\end{equation*}
From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p 0$. The \clt\ implies
that $\ocltb{t} (F_t - F) = O_p(1)$,
establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
and~\eqref{eq:13} are similar.
\end{proof}

\bibliography{texextra/references}
\end{document}
